Visual Inference for Goodness-of-Fit for A Network Model

### 2017-10-09 ASApaper/paper.Rmd
SAOMs + visinf

<!--Talk about visual inference-->
We propose to attack some of the aforementioned difficulties with SAOMs by using a technique known as *visual inference*. This technique was created by @Bujaetal to provide well-defined, statistical rigor to the usual exploratory data analyses and model diagnostics that are typically performed by visualizing the data as opposed to looking at it raw or gathering numerical summaries of it.

>>>>

<!--Talk about visual inference-->
We propose to attack some of the aforementioned difficulties with SAOMs by using a technique known as *visual inference*. This technique was created by @Bujaetal to provide well-defined, statistical rigor to the usual exploratory data analyses and model diagnostics that are typically performed by visualizing the data as opposed to looking at it raw or gathering numerical summaries of it. In visual inference there are *null plots* and *data plots*: the null plots are visualizations of data simulated from the model according to the null hypothesis, while the data plots are visualizations of data simulated from the model according to an alternative hypothesis. These two data sources are visualized side-by-side using small multiples using what Buja et al called the *lineup protocol*. The idea behind the lineup protocol is the police lineup, where witnesses to crimes are brought to the police station to observe a group of people, one of whom is suspected to have committed the crime, and are asked to identify the perpetrator of the crime. If the witness identifies the suspect in the lineup, that is taken as evidence the suspect is guilty, whereas if the witness does not identify the suspect, that is taken as evidence the suspect is not guilty. In the visual inference lineup protocol, the *suspect* is the data plot among $M-1$ null plots. If the "witness" can pick the data plot out of the lineup, that is taken as evidence that the null model should be rejected, whereas failing to pick out the data plot is taken as evidence that the null model should not be rejected. In our application of the lineup protocol to SAOMs, we include various effects of varying sizes in the SAOMs we fit to some data and try to *see* those effects in node-link diagram corresponding to simulations from the various models.
